General linear Models Coursework

### 2022-11-20 Draft_final.Rmd
Fixing error with final kable output table

```{r,echo=F}
#Producing table of results
knitr::kable(as.data.frame(tidy(lm.log.income.sqd)[,1:3]),digits=3,caption = "Estimated coefficients and SE for part 5 model")%>%
  row_spec(0,bold=T)%>%
  kable_styling(position = "center",latex_options = "HOLD_position")
```

@@

```{r,echo=F}
#Producing table of all exponentiated regession coefficients that are approx 1
knitr::kable(data.frame(tidy(lm.full.1.deletion)[14:22,1],exp(tidy(lm.full.1.deletion)[14:22,2])),digits=3)%>%
  row_spec(0,bold=T)%>%
  kable_styling(position = "center",latex_options = "HOLD_position")
```

@@

#Producing tables to display result
knitr::kable(data.frame("coefficent"=tidy(lm.final.model)[,1],
                 Point.estimates,
                 "Confidence Interval 95%"=c(paste("(",round(lwr,3),", ",round(upr,3),")")),
                 p.values),digits=3,caption = "Summary of exponentiated variables affecting expeniture")%>%
  row_spec(0,bold=T)%>%
  kable_classic(full_width=F,latex_options = "HOLD_position",position= "center")

@@

data.sex.household.CI <- data.frame(t(data.frame("Male"=male.CI, "Female"=female.CI)))%>%
  rename("1 Person"="X1",
         "2 Persons"="X2",
         "3 Persons"="X3",
         "4 Persons"="X4",
         "5+ Persons"="X5")

#creating table of 95% CI calculated
knitr::kable(data.sex.household.CI,digits=3,caption = "95% CI compared to male headed household of 1 person")%>%
  row_spec(0,bold=T)%>%
  column_spec(1,bold=T)%>%
  kable_styling(position = "center",latex_options = "HOLD_position")
```

>>>>

@@

```{r,echo=F}
#Producing table of all exponentiated regession coefficients that are approx 1
knitr::kable(data.frame(tidy(lm.full.1.deletion)[14:22,1],exp(tidy(lm.full.1.deletion)[14:22,2])),digits=3,caption="Coefficents of explantory variables with negliable affect on expenditure",)%>%
  row_spec(0,bold=T)%>%
  kable_styling(position = "center",latex_options = "HOLD_position", font_size = 7)
```

@@

#Producing tables to display result
knitr::kable(data.frame("coefficent"=tidy(lm.final.model)[,1],
                 Point.estimates,
                 "Confidence Interval 95%"=c(paste("(",round(lwr,3),", ",round(upr,3),")")),
                 p.values),digits=3,caption = "Summary of exponentiated variables affecting expeniture")%>%
  row_spec(0,bold=T)%>%
  kable_styling(full_width=F,latex_options = "HOLD_position",position= "center")

@@

#creating table of 95% CI calculated
data.frame(t(data.frame("Male"=male.CI, "Female"=female.CI)))%>%
  rename("1 Person"="X1",
         "2 Persons"="X2",
         "3 Persons"="X3",
         "4 Persons"="X4",
         "5+ Persons"="X5")%>%
  kable(caption = "95% CI compared to male headed household of 1 person",format = 'pandoc')
```

```{r,include=F}
# #creating table of 95% CI calculated
# kable(data.frame(data.sex.household.CI), caption = "95% CI compared to male headed household of 1 person")%>%
#   row_spec(0,bold=T)%>%
#   column_spec(1,bold=T)%>%
#   kable_classic(position = "center",latex_options = "HOLD_position")
# 
# knitr::kable(data.frame(tidy(lm.full.1.deletion)[14:22,1],exp(tidy(lm.full.1.deletion)[14:22,2])),digits=3)%>%
#   row_spec(0,bold=T)%>%
#   kable_styling(position = "center",latex_options = "HOLD_position")
```
